We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-08 paper/paper.tex
edit

To date, the tipicallity of satellite distributions can only be
addressed in simulations.
Most of the studies have been performed in the currently preferred
paradigm, which is based on a Cold Dark Matter cosmology in a expanding
Universe described by General Relativity including a Cosmological
Constant, the so-called Lambda Cold Dark Matter (LCDM) model.
The broad consensus is that these highly structured satellite distributions
are hard to find in simulations.  
There are still disagreements on the precise degree of atypicallity
and the conditions required to simulate satellite distributions closer.
These disagreements seem to be originated on what is considered to be
a LG analog in the simulation.

Some studies have focused on the study of individual dark matter halos
that could host galaxies like the MW or M31, while some other studies
have tried to simulate the formation of galaxy pairs resembling both
the MW and M31.
The transition from studying individual halos to pairs has been
motivated by the hypotesis hat the location of the Local Group in
the cosmic web should play a determinant role in building up planar
satellite distributions through preferential alignments and accretions
histories of galaxies.

>>>>

To date, the atipicallity of satellite distributions can only be
addressed in simulations.
Most of the studies have been performed in the currently preferred
paradigm, which is based on a Cold Dark Matter cosmology in a expanding
Universe described by General Relativity including a Cosmological
Constant, the so-called Lambda Cold Dark Matter (LCDM) model.
The broad consensus is that these highly structured satellite distributions
are hard to find in simulations.  
There are still disagreements on the precise degree of atypicallity
and the conditions required to simulate satellite distributions closer.
These disagreements seem to be originated on what is considered to be
a LG analog in the simulation.

Some studies have focused on the study of individual dark matter halos
that could host galaxies like the MW or M31, while some other studies
have tried to simulate the formation of galaxy pairs resembling both
the MW and M31.
The transition from studying individual halos to pairs has been
motivated by studies that show how the LG location in the cosmic web
plays a role in distingushing the the MW and M31 halos from the
average $\sim 10^{12}$ \Msun DM halo.

the cosmic web should play a determinant role in building up planar
satellite distributions through preferential alignments and accretions
histories of galaxies.
